### 2022-07-19 Papers/ICCC-2023/sections/design.tex
some more stuff
compiler structure image

\subsection{Design of the compiler}
\label{compiler-design}
\subsubsection{Frontend}

\subsubsection{Interpreter}

\subsubsection{Compiler interface}

\subsubsection{Backend}

>>>>

\subsection{Design of the compiler}
\label{compiler-design}

CTFE First compiler has four major components: Frontend, Interpreter, Compiler Interface and Backend.
Figure \ref{CTFE-first-compiler-structure} contains a diagram with an overview of how these pieces interact with eachother, during the compilaton process.
Frontend, described in chapter \ref{frontend}, parses the code in the compiled language and constructs its intermidaite representation, using interpreter's data structures.
It is used to analyze both user code and the Compiler Interface.
After the intermidiate representation is constructed, it is passed on to the Interpreter, which was described in chapter \ref{interpreter}.
Compiler Interface intermidiate representation is then executed, using the user program as data. 
This step converts the semantic model of the program into the backends intermidiate language.
This process has been further explained in chapter \ref{compiler-interface}.
Finaly the Backend generates the executable file.

\begin{figure}
	\includegraphics[height=10cm]{pictures/compiler-structure.png}
	\caption{CTFE First compiler structure}
	\label{CTFE-first-compiler-structure}
\end{figure}

\subsubsection{Frontend}
\label{frontend}

\subsubsection{Interpreter}
\label{interpreter}

\subsubsection{Compiler interface} 
\label{compiler-interface}

\subsubsection{Backend}
\label{backend}
